### 2025-04-21 thesis/thesis.tex
Add bibliography

\subsubsection*{RQ2 — Are there effective approaches against ambiguity in natural language input?}

@@

\subsubsection*{RQ3 — What are effective approaches for increasing semantic accuracy of queries?}

@@

% Theoretical Foundations
\section{Related Work}

@@

\begin{thebibliography}{99}
\bibitem{ref1} Author, A. (Year). Title of the reference. Journal/Publisher, Volume(Issue), Pages.
% Add more references as needed
\end{thebibliography}

@@

>>>>

\subsubsection*{RQ2 — What approaches are most effective in resolving ambiguity when translating natural language queries into SQL?}

@@

\subsubsection*{RQ3 — Which strategies are increasing semantic accuracy of queries?}

@@

% Theoretical Foundations
\section{Literature Review}

Test\cite{Atlas}

@@

@@

\nocite{*}

\bibliographystyle{apalike}
\bibliography{references}
